\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{tabularx}

\name{Thiago}{Roberto}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Fullstack Software Engineer}\end{center}
\begin{center}
\vspace{-0.3cm}
\begin{tabular}{c c c}
    \faMobile\hspace{0.1cm} 31971605029 \hspace{0.2cm} & \faEnvelope\hspace{0.1cm} \href{mailto:thiagorobertodc@outlook.com}{thiagorobertodc@outlook.com} \hspace{0.2cm} & \faHome\hspace{0.1cm} Belo Horizonte, Brazil \\
    \multicolumn{3}{c}{\faLinkedin\hspace{0.1cm} \href{https://www.linkedin.com/in/thiagorobertodc23/}{linkedin.com/in/thiago} \quad
    \faGithub\hspace{0.1cm} \href{https://github.com/thiagorobertodc}{github.com/thiago}}
\end{tabular}
\end{center}

\section{Experience}
\customcventry{Apr/2022 ‐ present}{{Nursa}}{Fullstack Software Engineer}{Salt Lake City, UT, USA (remote)}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\vspace{+0.1cm}\item Engaged in Nursa's payment module, helped build a robust instant payment system creating, testing and maintaning \textbf{API RESTful endpoints}. Code covered by \textbf{unit and integration tests with Jest}.
\item Mobile application features for the Shift Reports and Billing and Payments modules. Frontend with \textbf{Angular} and \textbf{React}. Backend with \textbf{Java}, \textbf{Spring Boot}, \textbf{Node.js} (Express.js) and \textbf{Nest.js}.
\item Developed a feature that improved the time to complete the Controlled Public Health Document (CDPH 530) by \textbf{200\%}, significantly reducing the time to allocate nursing staff to healthcare facilities.
\item Created a feature for daylight saving time transitions, ensuring that medical reports accurately reflect shift hours and preventing shifts from starting or ending during these transitions.
\end{itemize}}}

\vspace{+0.3cm}\customcventry{Aug/21 ‐ Apr/22}{{dti digital}}{Fullstack Software Engineer}{São Paulo, Brazil}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\vspace{+0.1cm}\item Developed a \textbf{web application} using \textbf{React.js} to manage documents and files related to iron mining structure extraction and maintenance.
\vspace{-0.1cm}\item Developed and maintained \textbf{endpoints} using \textbf{Java (Spring Boot)} and a Backend For Frontend (BFF). Managed a \textbf{NoSQL database} with \textbf{DynamoDB}. Ensured code coverage with \textbf{JaCoCo} and quality with \textbf{SonarCloud}.
\end{itemize}}}

\vspace{+0.3cm}\customcventry{Apr/21 ‐ Aug/21}{{Usemobile}}{Mobile Software Engineer}{Ouro Preto, MG, Brazil}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed \textbf{mobile applications} using \textbf{Flutter} and \textbf{React.js}, participating in decision-making processes and proposing ideas to consistently deliver product value.
\end{itemize}}}

\vspace{+0.2cm}\customcventry{Nov/19 ‐ Apr/21}{{dreamlabs}}{Mobile Development Intern}{Ouro Preto, MG, Brazil}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\vspace{+0.1cm}\item Developed various \textbf{mobile applications} at a software consultancy. As my first role in software engineering, I learned the fundamentals of programming tools and design patterns.
\vspace{+0.1cm}\item Applications developed using \textbf{React.js}.
\end{itemize}}}

\section{Education}
\customcventry{2016-2022}{Federal University of Ouro Preto}{Bachelor’s in Computer Science}{Ouro Preto, MG, Brazil}{}{}

\section{Skills and Tools}
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\vspace{+0.05cm}\item Version control with \textbf{Git}.
\vspace{+0.05cm}\item \textbf{Fluent communication in English}.
\vspace{+0.05cm}\item Backend: \textbf{Nest.js}, \textbf{Node.js}, \textbf{Java (Spring Boot)};
\vspace{+0.05cm}\item Frontend: \textbf{Angular}, \textbf{Ionic} and \textbf{React.js}. 
\vspace{+0.05cm}\item \textbf{Unit and integration testing} with \textbf{Jest}; coverage and quality with \textbf{SonarCloud}.
\vspace{+0.05cm}\item Secret key and value management in \textbf{AWS}.
\vspace{+0.05cm}\item \textbf{Azure DevOps} and \textbf{GitHub Actions} for application lifecycle management.
\vspace{+0.05cm}\item \textbf{RabbitMQ topics} and cron jobs for recurring events.
\vspace{+0.05cm}\item \textbf{Feature flags} for gradual releases.
\vspace{+0.05cm}\item \textbf{Docker} for application containerization to enhance development performance.
\vspace{+0.05cm}\item \textbf{DataDog} for log and metrics monitoring.
\vspace{+0.05cm}\item \textbf{PagerDuty} for support tickets.
\end{itemize}

\end{document}